Supplementary Information: Drought sensitivity is not a species trait: Tropical tree drought sensitivity is jointly shaped by drought characteristics, species adaptations, and individual microenvironments

### 2025-11-25 doc/response_to_reviewer_R3.Rmd

**RESPONSE: Thanks for your comments. We apologise for the confusion - the previous manuscript version was inadvertently linked to a private copy of the same file. We have now corrected this and updated the Zenodo repository (DOI: 10.5281/zenodo.15777975) with a manuscript that relies exclusively on the shared data csv files. As shown in the track-changes version, no content in the manuscript itself has been modified.**

**However, institutional policies of the Thai Long-Term Forest Ecological Research project prevent us from sharing some raw data files - specifically CTFSelev_hkk.rdata and the raw dendroband census information. We acknowledge that this limits full data availability, but all processing scripts for these raw data are now openly accessible in the repository. In particular, scripts 000_twi.R and 01_prepdata.R contain complete codes to process the raw dendroband census data and elevation data. These scripts output data csvs that are currently made public under data/dendro. To improve transparency, we have reorganised the scripts as *processing* and *analysis* scripts in different folders.**

**These processed datasets are now minimally sufficient to reproduce all the results through analysis scripts (01_species.R, 02_orderedcii.R, 03_orderedcii_tpi.R, 04_causal.R) and produce figures in the main text and SI (05_figures.R). Two SI figures (S4 and S8) that require raw data are exported from the data prep file (01_prepdata.R).**

### 2025-11-27 doc/response_to_reviewer_R4.Rmd

---
title: 'Responses to the Reviewer'
output: 
    bookdown::word_document2: 
    #   reference_docx: word-styles-reference.docx #make sure this line is indented! see this guide for formatting: https://rmarkdown.rstudio.com/articles_docx.html
      reference_docx: word-styles-reference-singlespace.docx #make sure this line is indented! see this guide for formatting: https://rmarkdown.rstudio.com/articles_docx.html
    #pdf_document:
    # engine: xelatex 
  #officedown::rdocx_document
bibliography: growth-precip-thailand.bib
# csl: new-phytologist.csl
csl: ecology-letters.csl 
suppress-bibliography: TRUE
---

Dear Editor,

We are pleased to submit a revised version of our manuscript, "Drought response is not a species trait: tropical tree drought sensitivity is shaped by drought characteristics, species adaptations, and individual microenvironments" (ELE-00826-2025) for consideration for publication in Ecology Letters. 
We have now addressed all of the Data Editor's comments and updated the repository. 
Specifically, we have addressed issues with dependencies in the files and ensured that all analysis code and the manuscript are executable.
Thank you for your patience with this process and we hope that this revision sufficiently meets the journal guidelines. 
We appreciate the thoroughness and the attention to detail with the data review process at Ecology Letters and the focus on achieving reproducible science and reusable data under global collaboration.

Thank you for considering this revised version for publication. 
We look forward to your response.

Sincerely,  
On behalf of all coauthors,  
Krishna Anujan

\newpage

## Referees' comments to the author(s):

### Referee: 1

Comments for the Authors
I understand your argument regarding permanent plots data, particularly in the Global South, as I am working with similar networks myself. I was waiting for a decision from the editor because it falls within the limits of Ecology Letters' requirements. However, I completely agree with your suggestion to share reproducible analyses with intermediary files. That said, this is still not the case. I managed to reproduce analyses 2, 3 and 4 by manually editing and fixing the codes, but not analyses 1 and 5. The object 'yrs' is missing from scripts 2, 3, 4 and 5 for them to work (because the environment is purged when the scripts are started). Furthermore, subdirectories for the plots and model outputs must be created in scripts 2, 3 and 4 before the analyses can be launched. You can either add these to the repository, or add an R line of code to create them (dir.create). For analysis 1, the table's junction will not work because there is no “Species” column in “median_incs” from “summaries_dataset.csv”. For analysis 5, I will leave you to search for the issue, as running the rest of the Bayesian model was already very time consuming. Before the next submission, please ensure that your codes are reproducible by downloading your GitHub repository again to an empty folder and checking that it is running correctly. That said, congratulations on your efforts to ensure the reproducibility of your analyses, which I believe will be of deep interest to researchers and students. I apologise in advance if you feel my review is too harsh, but it is thorough and I believe you are almost there. I really believe you are almost there. The small improvement you need will make all the difference to whether it is reused in future or not.

**RESPONSE: Thank you for your detailed response and for your understanding relating to collaborative, global science. We are also grateful for the attention to detail and the focus on meaningful reproducible science. We appreciate your patience with the multiple rounds here. We have now updated the Zenodo repository (DOI: 10.5281/zenodo.15777975) with dir.create codes, better initialisation (including code to download any missing packages) and removed all remaining calls to previous datasets. All scripts under scripts/analysis are now sequentially executable. We have also confirmed this, as you suggested, by downloading the repo and running things.**

**As you pointed out, the Bayesian analyses are slow and the outputs files are large, so we have also removed a few deprecated/redundant models which we had originally left in the scripts for completeness.**

**We hope that this revision now meets the journal requirements and also accepted guidelines on open science.**
